SST_patterns

### 2020-01-20 SST_patterns.Rmd
update
Added date column

# Does not accurately show the months
# Ned to include distance and product

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals)) +
  geom_line(aes(colour = product)) +
  geom_smooth(aes(colour = product), method = "lm") +
  facet_wrap(~site) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  facet_wrap(~site)+
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

>>>>

Combined_frequency <- Combined_frequency %>% 
  mutate(t = parse_date(date, format = "%b_%Y"),
         distance = factor(distance))

# Does not accurately show the months
# Plot need to include month_year, number of signals, distance and product ()

ggplot(data = Combined_frequency, aes(x = t, y = number_of_signals)) +
  geom_line(aes(colour = product)) +
  geom_smooth(aes(colour = product), method = "lm") +
  facet_wrap(~site) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

ggplot(data = Combined_frequency, aes(x = t, y = number_of_signals)) +
  geom_line(aes(colour = distance)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  facet_wrap(~site)+
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))
